Worflow

### 2017-06-02 R/workflow.Rmd
fix RSEC command

```{r datain}
#counts<-read.table("../data/oeCufflinkCountData.txt",sep="\t",header=TRUE)
core<-read.table("../data/oeCufflinkCountData_1000Var.txt",sep="\t",header=TRUE)
metadata<-read.table("../data/oeMetadata.txt",sep="\t",header=TRUE)
# load("../data/Expt4c2b_filtdata.Rda")
# load("../data/E4c2b_slingshot_wsforkelly.RData")
```

@@

```{r rsec_50}
fn = '../data/clustExp_W_k50.rda'
if(runClus) {
ceObj <- RSEC(t(W), k0s = 4:15, alphas = c(0.1), betas = 0.8,
                      clusterFunction = "hierarchical01", minSizes=1,
                      sequential = TRUE, subsample = TRUE, ncores = NCORES,
					  combineProportion = 0.7,mergeMethod = "locfdr", mergeCutoff = 0.01
                      subsampleArgs = list(resamp.num=100,
                                           clusterFunction="kmeans",
                                           clusterArgs=list(nstart=10)),
                      seqArgs = list(k.min=3, top.can=5), verbose=TRUE)
save(ceObj, file = fn)
}
else{
	load(fn)
}
```

>>>>

EAP: zinbFit doesn't accept data.frame objects, so currently have to have a `data.matrix` command. Should it be changed so that it does?

```{r datain}
#counts<-read.table("../data/oeCufflinkCountData.txt",sep="\t",header=TRUE)
core<-read.table("../data/oeCufflinkCountData_1000Var.txt",sep="\t",header=TRUE)
core<-data.matrix(core)
metadata<-read.table("../data/oeMetadata.txt",sep="\t",header=TRUE)
# load("../data/Expt4c2b_filtdata.Rda")
# load("../data/E4c2b_slingshot_wsforkelly.RData")
```

@@

```{r rsec_50}
fn = '../data/clustExp_W_k50.rda'
if(runClus) {
ceObj <- RSEC(t(W), k0s = 4:15, alphas = c(0.1), betas = 0.8,
                      clusterFunction = "hierarchical01", minSizes=1,
                      ncores = NCORES,
					  combineProportion = 0.7,mergeMethod = "locfdr", mergeCutoff = 0.01
                      subsampleArgs = list(resamp.num=100,
                                           clusterFunction="kmeans",
                                           clusterArgs=list(nstart=10)),
                      seqArgs = list(k.min=3, top.can=5), verbose=TRUE)
save(ceObj, file = fn)
}
else{
	load(fn)
}
```
